The imprint of global magma oceans on exoplanet demographics

### 2022-09-28 src/tex/ms.tex
change instellation to new value

\begin{note}
    The power from the host star per unit area at the position of a planet or stellar insolation $S$ in units of Earth's insolation is given by
    \begin{equation}
        \frac{S}{S_\oplus} = \left(\frac{L_\star}{L_\odot}\right) \left(\frac{au}{a}\right)^2 .
    \end{equation}

    We further define the solar-equivalent semi-major axis $a_{eff} = a (L_\star/L_\odot)^{-1/2}$, at which a planet experiences the same insolation as a Solar System planet at an orbital distance~$a$.
\end{note}

@@

    Another potential false positive contribution comes from the "Neptune desert``, a triangular region of low planet occurrence density of close-in planets in period-radius space~\citep{Szabo2011,Mazeh2016,Dreizler2020b}.
    The shape of this region is such that smaller planets become less frequent the closer to the star they are, which to some degree resembles the pattern introduced by the insolation dependency of the magma ocean probability.
    \todo{explore if this can cause confusion}
    \todo{is there overlap/confusion with the radius/density trend in \citet{Luque2022b}?}
\end{note}

>>>>

\begin{note}
    The power from the host star per unit area at the position of a planet or instellation $S$ in units of Earth's insolation is given by
    \begin{equation}
        \frac{S}{S_\oplus} = \left(\frac{L_\star}{L_\odot}\right) \left(\frac{au}{a}\right)^2 .
    \end{equation}
    Here, we assume global redistribution of incoming flux and a fixed albedo of $0.3$, comparable to Earth's [CITE].
    The absolute value of $S_\oplus$, by which all synthetic planets are scaled, is then \SI{238}{\watt\per\square\meter}.
    We further define the solar-equivalent semi-major axis $a_{eff} = a (L_\star/L_\odot)^{-1/2}$, at which a planet experiences the same instellation as a Solar System planet at an orbital distance~$a$.
\end{note}

@@

    Another potential false positive contribution comes from the "Neptune desert``, a triangular region of low planet occurrence density of close-in planets in period-radius space~\citep{Szabo2011,Mazeh2016,Dreizler2020b}.
    The shape of this region is such that smaller planets become less frequent the closer to the star they are, which to some degree resembles the pattern introduced by the instellation dependency of the magma ocean probability.
    \todo{explore if this can cause confusion}
    \todo{is there overlap/confusion with the radius/density trend in \citet{Luque2022b}?}
\end{note}
